Open Data for _Crime and Place_ Research: A Practical Guide in R.

### 2020-11-19 manuscript.Rmd
revisions update scholar

Secondly, despite the merits of open data in terms of remedying pitfalls in traditional survey methods, there are other threats to validity that may emerge. For instance, whilst many online resources offer an 'honest' depiction of society, uncaptured by surveys, researchers should be careful in interpreting people's communication online as completely authentic [@manovich2011trending]. This could be a result of individuals willingly managing and 'curating' their online presence [@ellison2006managing], or because of wider issues such as government censorship, or cultural norms around particular topics, particularly sensitive topics of interest to researchers of crime, such as sexual assault or drug use.

Relatedly, researchers should be aware of issues over sampling, and ultimately, the generalizability of findings that emerge from the analysis of open data. In the case of crowdsourced data, the sample is not randomly drawn from a population, but rather, it is self-selected, giving way for people willing to discuss or contribute to a particular issue, which introduces a degree of bias [@longley2012geodemographics]. Specifically, contributors tend to be men, between the ages of 20-50, with a college or university degree [@budhathoki2010participants; @haklay2010good]. Contributions to resources such as Open Street Map (which we look at in the practical exercise) are correlated with contextual characteristics such as poverty and population density, and as such, coverage is non-uniformly distributed across urban areas [@mashhadi2013putting]. These are important to keep in mind (and be transparent about) when reporting findings based on analysis of such data.

>>>>

Secondly, the validity and reliability of open data sources can be questioned, and some cases, difficult to verify. For instance, Open Street Map (which we look at in the practical exercise) contains a vast array of data about its features, from whether a bar is LGBTQ+ friendly, to whether a train station is wheelchair accessible. Often, there is no method for cross-validating this information with other data sources. Similarly, whilst many open resources offer a depiction of society uncaptured by traditional surveys (e.g. social media) researchers should be careful in interpreting people's communication online as completely authentic [@manovich2011trending]. This could be a result of individuals willingly managing and 'curating' their online presence [@ellison2006managing], or because of wider issues such as government censorship, or cultural norms around certain topics, particularly sensitive topics of interest to researchers of crime, such as sexual assault or drug use.

Relatedly, researchers should be aware of issues over sampling and selection, and ultimately, the generalizability of findings that emerge from the analysis of open data. In the case of crowdsourced data, the sample is not randomly drawn from a population, but rather, it is self-selected, giving way for people willing to discuss or contribute to a particular issue, which introduces a degree of bias [@longley2012geodemographics]. Specifically, contributors tend to be men, between the ages of 20-50, with a college or university degree [@budhathoki2010participants; @haklay2010good]. Contributions to resources such as Open Street Map are correlated with contextual characteristics such as poverty and population density, and as such, coverage is non-uniformly distributed across urban areas [@mashhadi2013putting]. These are important to keep in mind (and be transparent about) when reporting findings based on analysis of such data.

### 2020-11-19 supplementary_materials.Rmd
revisions update scholar

```{r, eval = F}
# Retrieve Stratford buffer from Open Street Map.
stratford_osm_sf <- osm_jub_sf %>% 
  filter(name == "Stratford")

@@

# Visualize the building footprints, Open Street Map buffer, TfL buffer, and crime
# locations. Note that the single point for the crimes is due to the approximation!
# There are actually multiple crimes. Colors have been manually selected
# from the viridis package to be easier to read by those with colorblindness.
ggplot() +
  geom_sf(data = strat_fp_poly_sf, fill = "black") +
  geom_sf(data = stratford_osm_sf, fill = "#440154FF", alpha = 0.3) +
  geom_sf(data = stratford_tfl_sf, fill = "#FDE725FF", alpha = 0.3) +
  geom_sf(data = strat_osm_btp_sf, col = "#3CBC75FF", fill = "white") +
  theme(axis.text = element_text(size = 6))
```

@@

This quick check has shed some light on what is happening. The buffer generated from the TfL station location (in yellow) covers a different part of the station to the Open Street Map buffer (in blue). The latter covers most of the main station building, while the former centers around the platforms to the north. Because the British Transport Police crime locations have been geocoded to a location in the main station building (in green) the TfL buffer has missed them. If we had used a larger buffer, it is likely that the TfL location would have captured the crime cluster, but then we would increase the risk of picking up crimes outside of the station. In many cases, there will not be an obvious 'right or wrong' answer to determine which open data source is most appropriate, but investigations like this one will help inform the decision. We might consider investigating other stations before deciding on which data to use, and ensure that findings are reported transparently with reference to these discussions.

>>>>

```{r stratford, eval = F}
# Retrieve Stratford buffer from Open Street Map.
stratford_osm_sf <- osm_jub_sf %>% 
  filter(name == "Stratford")

@@

# Visualize the building footprints, Open Street Map buffer, TfL buffer, and crime
# locations. Note that the single point for the crimes is due to the approximation!
# There are actually multiple crimes. Colors have been manually selected
# from the viridis package simply to identify each object individually.
ggplot() +
  geom_sf(data = strat_fp_poly_sf, fill = "black") +
  geom_sf(data = stratford_osm_sf, fill = "#440154FF", alpha = 0.3) +
  geom_sf(data = stratford_tfl_sf, fill = "#FDE725FF", alpha = 0.3) +
  geom_sf(data = strat_osm_btp_sf, col = "#3CBC75FF", fill = "white") +
  theme(axis.text = element_text(size = 6))
```

@@

This quick check has shed some light on what is happening. The buffer generated from the TfL station location (in yellow) covers a different part of the station to the Open Street Map buffer (in blue). The latter covers most of the main station building, while the former centers around the platforms to the north. Because the British Transport Police crime locations have been geocoded to a location in the main station building (in green) the TfL buffer has missed them. If we had used a larger buffer, it is likely that the TfL location would have captured the crime cluster, but then we would increase the risk of picking up crimes outside of the station. This also serves to highlight the limitations of the open crime data, because we cannot discern the _exact_ location of these crimes in the station. It is in fact plausible that some of these crimes did occur in the TfL buffer, but due to the process of anonymization, the points have been snapped the main station building.

In many cases, there will not be an obvious 'right or wrong' answer to determine which open data source is most appropriate, but investigations like this one will help inform the decision. We might consider investigating other stations before deciding on which data to use, and ensure that findings are reported transparently with reference to these discussions.
